---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  message = FALSE,
  warning = FALSE,
  comment = "#>",
  fig.path = "README-"
)
```

# completejourney

[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![Travis-CI Build Status](https://travis-ci.org/bradleyboehmke/completejourney.svg?branch=master)](https://travis-ci.org/bradleyboehmke/completejourney)

## Overview

An R data package that provides access to data in the Complete Journey Study 
provided by [84.51°](http://www.8451.com). The data represents grocery store 
shopping transactions over one year from a group of 2,469 households who are 
frequent shoppers at a retailer. It contains all of each household's purchases, 
not just those from a limited number of categories. For certain households, 
demographic information as well as direct marketing contact history are included. 

* `transactions_sample`: a sampling of the products purchased by households
* `products`: product metadata (brand, description, etc.)
* `demographics`: household demographic data (age, income, family size, etc.)
* `campaigns`: campaigns received by each household
* `campaign_descriptions`: campaign metadata (length of time active)
* `coupons`: coupon metadata (UPC code, campaign, etc.)
* `coupon_redemptions`: coupon redemptions (household, day, UPC code, campaign)
* `promotions_sample`: a sampling of the product placement in mailers and in stores corresponding to advertising campaigns

## Installation

You can install `completejourney` from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("bradleyboehmke/completejourney")
```

```{r load-pkg}
library(completejourney)
```

## Downloading full data sets

Due to the size of the transactions and promotions data, the package provides a
sampling of the data built-in with `transactions_sample` and `promotions_sample`. 
However, you can access the full promotions and transactions data sets from the 
source GitHub repository with the following: 

```{r load-transactions}
# get the full transactions data set
transactions <- get_transactions()
transactions
```

```{r load-promotions}
# get the full promotions data set
promotions <- get_promotions()
promotions
```

```{r load-both}
# a convenience function to get both
c(promotions, transactions) %<-% get_data(which = 'both', verbose = FALSE)
dim(promotions)
dim(transactions)
```

## Learn more

Learn more about the completejourney data, and the type of insights you can look for, at [http://bit.ly/completejourney](https://bradleyboehmke.github.io/completejourney/).

## Source

The Complete Journey data is available at: http://www.8451.com/area51/.
