---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# completejourney

[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![Travis-CI Build Status](https://travis-ci.org/bradleyboehmke/completejourney.svg?branch=master)](https://travis-ci.org/bradleyboehmke/completejourney)

## Overview

An R data package of the Complete Journey Study provided by [84.51](http://www.8451.com). 
The data represents retail shopping transactions over two years from a group of 2,500 households who are frequent shoppers at a retailer. It contains all of each household's purchases, not just those from a limited number of categories. For certain households, demographic information as well as direct marketing contact history are included. The package comes with the following datasets: 

* `transactions`: products purchased by households
* `products`: product metadata (brand, description, etc.)
* `demographics`: household demographic data (age, income, family size, etc.)
* `campaigns`: campaigns received by each household
* `campaign_descriptions`: campaign metadata (length of time active)
* `coupons`: coupon metadata (UPC code, campaign, etc.)
* `coupon_redemptions`: coupon redemptions (household, day, UPC code, campaign)
* `product_placements`: product placement in mailers and in stores corresponding to advertising campaigns

## Installation

You can install `completejourney` from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("bradleyboehmke/completejourney")
```

## Source

The Complete Journey data is available at: http://www.8451.com/area51/.
